ISSP 2009 - Salary Gap & meritocracy

### 2019-06-22 files/20190608_ISSP09juitsa.Rmd
Update 20190608_ISSP09juitsa.Rmd
junio 10 FACSO

---
title: 'ISSP 2009 - Salary Gap & meritocracy'
author: "Julio César Iturra Sanhueza - jciturra@uc.cl"
output: html_document
---

@@

```{r }
{
  library(haven)
  library(dplyr)
  library(here)
  library(sjlabelled)
  library(sjPlot)
  library(ggplot2)
  library(knitr)
  library(kableExtra)
}
```

```{r data, include=FALSE}
issp09<- read_dta(file = here("data","ZA5400_v4-0-0.dta"))

sjPlot::view_df(issp09,max.len = 45)
options(scipen=999)
```

@@

@@

@@

table2<- salarios %>% group_by(Pais=as_factor(pais)) %>% summarise(M=mean(lngap_just,na.rm = TRUE), 
                                                                      ME=median(lngap_perc,na.rm = TRUE),
                                                                      SD=sd(lngap_perc,na.rm = TRUE),
                                                                      Min=min(lngap_perc,na.rm = TRUE),
                                                                      Max=max(lngap_perc,na.rm = TRUE))

>>>>

---
title: 'ISSP 2009 - Salary Gap & meritocracy'
author: "Julio César Iturra Sanhueza - jciturra@uc.cl"
output: 
html_document: 
code_folding: show
---

@@

```{r }
{
  library(dplyr)
  library(here)
  library(sjlabelled)
  library(sjPlot)
  library(ggplot2)
  library(knitr)
  library(kableExtra)
}
```

@@

<button href="#tabla1" data-toggle="collapse" style="text-align: right;">Tablas</button>

<div id="tabla1" class="collapse">

@@

</div>

@@

table2<- salarios %>% group_by(Pais=as_factor(pais)) %>% summarise(M=mean(lngap_just,na.rm = TRUE), 
                                                                      ME=median(lngap_just,na.rm = TRUE),
                                                                      SD=sd(lngap_just,na.rm = TRUE),
                                                                      Min=min(lngap_just,na.rm = TRUE),
                                                                      Max=max(lngap_just,na.rm = TRUE))
